---
title: "ST3233 Tutorial 1 Solution"
author: "Chen Penghao (A0122017Y)"
date: "28 August 2017"
output:
  pdf_document: default
  html_document: default
---
### Preliminary:
```{r}
library(fpp2)
```

## Question 1: plot the graph
```{r}
fmri_data <- read.table("fmri.dat.txt")
fmri_ts <- ts(fmri_data[,2], deltat = 2, frequency=0.5, start=1)

plot(fmri_ts, xlab="Time (seconds)", ylab="Signal Intensity",
     main="MRI (Cortex)", col="coral3")
abline(v=seq(0, 256, by=32), col="grey", lty=2)
```

## Question 2: Discussion
The data exhibits strong seasonal patterns every 32 seconds, which corresponds to the time where stimualtes are set in or taken away. 


## Question 3: Season plot
```{r}
seasonplot(fmri_ts, s=32, main="MRI Season Plot", xlab="Season", ylab="Signal Intensity", 
           col=1:4, year.labels.left=TRUE, year.labels=TRUE)

legend("topright",legend=paste("Period ", 1:4, sep=""), col=1:4, lwd=TRUE)
```


### Question 4: Seasonal subseries plot
```{r}
fmri_ts = ts(fmri_data[,2], start=1, frequency=32)
monthplot(fmri_ts, main="MRI Seasonal Subseries Plot", ylab="Signal Intensity",
          xlab="Season", col.base='blue')
```

# Matching Time Plots to Lag Plots
* The data has no apparent trend as a whole.
* It exhibits some seasonal patterns especially when time is less than 200 seconds, where x reaches the crest in approximately equal time interval.
* The value of x reaches its peak when time is approximately 270, and a clear downward trend is observed when 270 < time < 370.
* Overall x would be more similar to the pattern of a Random Walk model, where each time the change in value of x would be correlated to the previous one plus a residual that follows the distribution of a White Noise.
* The value of y exhibits characteristics of White Noise.

* Hence a would be referring to y, where b is referring to x.
