---
title: "ST3233 Tutorial 3 Solution"
author: "Chen Penghao"
date: "11 Sept 2017"
output:
  html_document: default
  pdf_document: default
---

###Read the data and state the start and end dates
```{r}
instant_noodles_data <- read.table("instant_noodles.txt", header = TRUE)
unadjusted_price = ts(instant_noodles_data[,2], start = 1993, frequency = 12)
pr_1993 = ts(instant_noodles_data[,3], start = 1993, frequency = 12)
cpi = ts(instant_noodles_data[,4], start = 1993, frequency = 12)
```

Start date: Jan 1993

End date: Apr 2017

According to the information, we have:

```{r}
past_cpi = window(cpi, start=c(2016, 5))
forecast_cpi = past_cpi * 1.01
```

###Forecast using benchmark methods

####Random Walk with Drift
```{r}
library(fpp2)
instant_rwf <- rwf(pr_1993, 12, drift=TRUE)
residual_rwf <- instant_rwf$residuals
checkresiduals(instant_rwf, test=FALSE)
plot (instant_rwf,main =" Price of Instant Noodles Random Walk with Drift", xlab =" Year ",
PI= FALSE )
```

####Average Method
```{r}
library(fpp2)
instant_meanf <- meanf(pr_1993, 12,)
residual_meanf <- instant_meanf$residuals
checkresiduals(instant_meanf, test=FALSE)
plot (instant_meanf,main =" Price of Instant Noodles Using Mean Method", xlab =" Year ",
PI= FALSE )
```

####Naive Method
```{r}
library(fpp2)
instant_naive <- naive(pr_1993, 12)
residual_naive <- instant_naive$residuals
checkresiduals(instant_naive, test=FALSE)
plot (instant_naive,main =" Price of Instant Noodles Using Naive Method", xlab =" Year ",
PI= FALSE )
```

####Seasonal naive
```{r}
library(fpp2)
instant_snaive <- snaive(pr_1993, 12)
residual_snaive <- instant_snaive$residuals
checkresiduals(instant_snaive, test=FALSE)
plot (instant_snaive,main =" Price of Instant Noodles Using Seasonal Naive Method", xlab =" Year ",
PI= FALSE )
```


###Forecast using unadjusted prices
####Random Walk with Drift
```{r}
library(fpp2)
unadj_rwf <- rwf(unadjusted_price, 12, drift=TRUE)
residual_rwf <- unadj_rwf$residuals
checkresiduals(unadj_rwf, test=FALSE)
```

####Average Method
```{r}
library(fpp2)
unadj_meanf <- meanf(unadjusted_price, 12,)
residual_meanf <- unadj_meanf$residuals
checkresiduals(unadj_meanf, test=FALSE)
```

####Naive Method
```{r}
library(fpp2)
unadj_naive <- naive(unadjusted_price)
residual_naive <- unadj_naive$residuals
checkresiduals(unadj_naive, test=FALSE)
```

####Seasonal naive
```{r}
library(fpp2)
unadj_snaive <- snaive(unadjusted_price, 12)
residual_snaive <- unadj_snaive$residuals
checkresiduals(unadj_snaive, test=FALSE)
```

### US GDP
```{r}
transf_gdp_3 <- BoxCox(usgdp, lambda = 3)
transf_gdp_2 <- BoxCox(usgdp, lambda = 2)
transf_gdp_1 <- BoxCox(usgdp, lambda = 1)
transf_gdp_log <- BoxCox(usgdp, lambda = 0)
transf_gdp_i1 <- BoxCox(usgdp, lambda = -1)
transf_gdp_i2 <- BoxCox(usgdp, lambda = -2)
plot(transf_gdp_3)
plot(transf_gdp_2)
plot(transf_gdp_1)
plot(transf_gdp_log)
plot(transf_gdp_i1)
plot(transf_gdp_i2)
```

Log transformation is the most suitable.


```{r}
forecast_gdp_log <- BoxCox(usgdp, lambda = 0)
forecast_mean <- rwf(forecast_gdp_log, drift=TRUE)$mean
back_transform_median_log <- exp(forecast_mean)
plot(usgdp, col=1)
lines(back_transform_median_log, col=2)
```

```{r}
drift_param <- BoxCox.lambda(usgdp)
```

drift parameter = 0.36635

```{r}
forecast_gdp <- BoxCox(usgdp, lambda = drift_param)
forecast_mean <- rwf(forecast_gdp, drift=TRUE)$mean
back_transform_median <- forecast_mean ^ (1/drift_param)
plot(usgdp, include =200)
lines(back_transform_median, col=5)
```
