---
title: "ST3233 Tutorial 1 Solution"
author: "Chen Penghao (A0122017Y)"
date: "28 August 2017"
output:
  pdf_document: default
  html_document: default
---
### Preliminary:
```{r}
library(fpp2)
```

## Question 1: plot the graph
```{r}
x_data <- read.table("company_X.txt")
x_ts <- ts(x_data, start = 1967, frequency =13)
plot(x_ts, ylab = "sales", xlab = "year", main = "Company X Sales")
```
There is strong seasonal effect, no obvious overall trends or cycles.

## Question 2: Extract data
```{r}
x_ts_2 <- window(x_ts, start = c(1967,5), deltat = 1) #every year
plot(x_ts, ylab = "sales", xlab = "year", main = "Company X Sales")
lines(x_ts_2, col = 'red', type = 'b')
legend('topright', col = c('red', 'black'), lty = 1, pch = c(1,NA), legend = c("Subseries", "Full"), cex = 0.8)
```



## Question 3: Which season have changed the most, and which the least?
```{r}
monthplot(x_ts)
```

We wish to see which season has changed the most, we make seasonal subseries plot to single out every season

### Question 4: Seismic Activity
```{r}
ea <- read.table("earthquake.txt", skip = 1)
ea <- ts(ea, frequency = 1)
plot(ea)
ea1 <- window(ea, end = 1024)
ea2 <- window(ea, start = 1025)
boxplot(ea1, ylim = c(-0.5, 0.5), main = "Period 1")
boxplot(ea2, ylim = c(-0.5,0.5), main = "Period 2")
```
We can see that the variability of the two portions differs drastically.


