---
title: "ST3233 Tutorial 5 Solution"
author: "Chen Penghao"
date: "2 Oct 2017"
output:
  html_document: default
  pdf_document: default
---

# Company X Data

$y_t = T_t + S_t + R_t$

# 1. Estimate 

```{r}
library(fpp2)
ff <- c(1/3, 1/3, 1/3)
x_data <- read.table("company_X.txt")
x_ts <- ts(x_data, start = 1967, frequency = 13)

x_d <- decompose(x_ts, type="additive", filter=ff)
plot(x_d)

x_trend <- x_d$trend
plot(x_ts)
lines(x_trend, col = 'red')

x_seasonadj <- seasadj(x_d)
lines(x_seasonadj, col = 'blue')
```



# Plastics Data
```{r}
ts.plot(plastics)
```
There is seasonal pattern across each time period where the trend first goes up, reaches a peak, and then eventually goes down. The overall trend is going towards upwards.

```{r}
p_d <- decompose(plastics, type = "multiplicative")
p_trend <- trendcycle(p_d)
p_ss <- seasonal(p_d)
plot(p_d)
plot(p_trend, col = 'red')
plot(p_ss, col = 'blue')

p_sa <- seasadj(p_d)
plot(plastics)
lines(p_sa, col = 'green')

p_copy <- plastics
p_copy[35] = 0
plot(p_copy)
p_sa2 <- seasadj(decompose(p_copy))
lines(p_sa2, col = 'green')

p_copy2 <- plastics
p_copy2[60] = 0
plot(p_copy2)
p_sa3 <- seasadj(decompose(p_copy2))
lines(p_sa3, col = 'green')
```
The seasonally adjusted line appears more jerky and the outlier does affect the shape of the seasonally adjusted line.
Having an outlier at the end is different from having one in the middle when using classical decomposition method.

# Theoretical Questions

## Question 1

First iteration: $y'_t = \frac{1}{5}\left (y_{t-2} + y_{t-1} + y_t + y_{t+1} + y_{t+2} \right)$

Second iteration: $y''_t = \frac{1}{3}\left (y'_{t-1} + y'_t + y'_{t+1} \right)$
